---
title: "package-development"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### recommended libraries
library(devtools)
library(tidyverse)
library(fs)
```

## Create package directory

This is just to be run once, behind the scenes.

```{r}
#create_package(path = 'C:/Projects/Github/foofactors')
```

This created a number of files:
(*) .Rbuildignore -- lists files needed but not to be included in final built package.
(*) .Rproj.user -- internal RStudio directory.
(*) .gitignore -- ignores behind-the-scenes files from R and RStudio when pushing to Git.
(*) DESCRIPTION -- Metadata file
(*) NAMESPACE -- declares functions to be exported and functions needed to be imported to function.
(*) R/ -- contains .R files with function definitions.
(*) foofactors.Rproj -- RStudio project file.

## Initializing Git

Similar to package creation, this initializes Git relationship and creates an initial commit. Can include commit message.

```{r}
#use_git()
```

## Writing first functions

```{r}
## See how factors play together
(a <- factor(c('character', 'hits', 'your', 'eyeballs')))
(b <- factor(c('but', 'integer', 'where it', 'counts')))
c(a, b)

## concatenate those properly!
factor(c(as.character(a), as.character(b)))

## create the function to do this
fbind <- function(a, b) {
  factor(c(as.character(a), as.character(b)))
}
```


