---
title: "package-development"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### recommended libraries
library(devtools)
library(tidyverse)
library(fs)
```

## Create package directory

This is just to be run once, behind the scenes.

```{r}
#create_package(path = 'C:/Projects/Github/foofactors')
```

This created a number of files:

* `.Rbuildignore` -- lists files needed but not to be included in final built package.
* `.Rproj.user` -- internal RStudio directory.
* `.gitignore` -- ignores behind-the-scenes files from R and RStudio when pushing to Git.
* `DESCRIPTION` -- Metadata file
* `NAMESPACE` -- declares functions to be exported and functions needed to be imported to function.
* `R/` -- contains .R files with function definitions.
* `foofactors.Rproj` -- RStudio project file.

## Initializing Git

Similar to package creation, this initializes Git relationship and creates an initial commit. Can include commit message.

```{r}
#use_git()
```

## Writing first functions

```{r}
## See how factors play together
(a <- factor(c('character', 'hits', 'your', 'eyeballs')))
(b <- factor(c('but', 'integer', 'where it', 'counts')))
c(a, b)

## concatenate those properly!
factor(c(as.character(a), as.character(b)))

## create the function to do this
#fbind <- function(a, b) {
#  factor(c(as.character(a), as.character(b)))
#}
```

`fbind` was written to `fbind.R` in the `R/` folder. We can test it using:

* `use_r('fbind')`
* `load_all()`

The function does not show up in the environment, however, as this simulates loading a library (e.g., `library(foofactors)`).

```{r}
load_all()
```


Use `check()` to verify everything is in working order.

This outputs 2 warnings:

1. `Non-standard license specification`
2. `Undocumented code objects: 'fbind'`

And 1 note:

1. `Non-standard file/directory found at top level: 'foofactors.Rmd'`

We can add a standard license via `use_mit_license('Todd Ellis')` to solve 1. 

The latter requires creating a .Rd file with markup language offering details on the function, but we can use the Roxygen2 library to do this int he .R file itself.

See top of `fbind.R` for an example. Once written, run with `document()`.

Once that's done, run `check()` again, and then `install()`.

Reset R or empty the workspace and then we can use the library as it is in R:

```{r}
library(foofactors)

a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))

fbind(a, b)
```

It works! We can now create unit tests (not really sure what this mean...) by using `use_testthat()`.

This creates empty test files for us to fill.

Create a test file using:

* `use_test('fbind')`

Then run the test (and all other test files in the package) using `test()` or `check()`.

```{r}
library(testthat)
load_all() # load tests
test()
```

## Using other packages

Use `use_package()` to make calls to other packages. *All* used packages need to be pulled, including base tools like the stats or utils libraries.

Our next function uses part of the `forcats` library.

```{r}
#use_package('forcats')
#use_r('fcount')
```

This throws an import reference to the description file, and creates a new .R file for the function `fcount()`.

```{r}
load_all()
fcount(iris$Species)
```

This stage was uploaded to our Github repo, and we can now edit a README.Rmd file using `use_readme_rmd()`.

Once finishing edits on the .Rmd file, run `rmarkdown::render('README.Rmd')` to render the .md file for GitHub. This needs to be run anytime the .Rmd file is edited.

*Note*: Since this tutorial started, updates to the tidyverse using the `vctrs` package led to errors here in package dependencies and I had to manually delete the past installation.

